---
title: "Initial Korean covid 19"
author: "Connor Rice"
date: "Fall 2023"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
install.packages("gridExtra")
require(tidyverse)
require(tigerstats)
require(lubridate)
library(gridExtra)
krdata <- read.csv(file = 'kRdata.csv')
krdata <- krdata %>%
mutate(across(where(is.character), as.factor))
```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?






## Graphical results - use ggplot commands to do this  

```{r}
plot_counts <- barchartGC(~Sex + result, data = krdata,
           main = "Comparison of Sex and Outcome(#)",
           xlab = "Sex", ylab = "#")

plot_percentages <- barchartGC(~Sex + result, data = krdata, type = "percent",
           main = "Comparison of Sex and Outcome(%)",
           xlab = "Sex", ylab = "Percentage")

grid.arrange(plot_counts, plot_percentages, ncol = 2)
```
  
## Numerical results

```{r}
table1 <- xtabs(~Sex + result, data=krdata)
rowPerc(table1)
colPerc(table1)
```

## Inferential results 




## Conclusions

