---
title: "Initial Korean covid 19"
author: "Connor Rice"
date: "Fall 2023"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
install.packages("gridExtra")
require(tidyverse)
require(tigerstats)
require(lubridate)
library(gridExtra)
krdata <- read.csv(file = 'kRdata.csv')
krdata <- krdata %>%
mutate(across(where(is.character), as.factor))
```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?

The data will be analysed by use of code blocks from the Cat~Cat helper file that have been edited to work for the data. Data will be examined with the intent of determining if there is a significant difference in case outcome of Covid patients, in terms of fatal or non-fatal, based on the sex of the patient.

$H_0$ There is no difference between Covid fatal/non-fatal outcomes based on Sex
$H_A$ There is a statistical difference between Covid fatal/non-fatal outcomes based on Sex  

## Graphical results - use ggplot commands to do this  

```{r}
plot_counts <- barchartGC(~result + Sex, data = krdata, main = "Comparison of Sex and Outcome(#)", xlab = "Outcome", ylab = "Number")

plot_percentages <- barchartGC(~result + Sex, data = krdata, type = "percent", main = "Comparison of Sex and Outcome(%)",xlab = "Outcome", ylab = "Percentage")

grid.arrange(plot_counts, plot_percentages, ncol = 2)
```
  
## Numerical results

```{r}
table1 <- xtabs(~Sex + result, data=krdata)
rowPerc(table1)
colPerc(table1)
```

## Inferential results 

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

## Conclusions

